Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-26 paper/ms.tex
update manuscript

\tn\ joins a number of other young planetary systems reported from
TESS, including DS Tuc Ab \citep{newton_tess_2019}, HIP 67522
\citep{rizzuto_tess_2020}, and TOI 1726 \citep{mann_tess_2020}.

Rossiter measurements will confirm.

After, a mass measurement should be worthwhile.

We'll get more TESS data in January(?).

I don't strongly expect the Veloce RVs or the FEROS ones to lead to a
mass measurement. The reason is that with vsini=17km/s, and 2\%
rotation amplitude signal, we expect an RV RMS of 300m/s at the
Prot=3.5 day rotation period (vsini*rotation amplitude). This is
probably larger than the expected planet signal (100m/s, 8 days).

>>>>

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}
However, unlike these planets, \pn\ is validated but not yet confirmed.

The easiest path towards definitively confirming
whether \tn\ is a planet will be a Rossiter-McLaughlin (RM) measurement.  
Detection of the RM signal
would rule out BEB and HEB scenarios, as it would imply that the
eclipsing object is bound to the target star. Combined with our
non-detection of the planet's mass from radial velocity monitoring,
this would confirm that \pn\ is a planet.

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{winn_exoplanet_2010}
\begin{equation}
  \Delta V_{\rm RM} \approx \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 21\,{\rm m\,s}^{-1},
\end{equation}
where we have assumed stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}, and for
calculation purposes we assumed $b=0.95$.  This is challenging, but
for a 1.9$\,$hr transit of a $V=10.6$ star, a detection could be achieved
with modern spectrographs.  The next viable total transit windows from
Chile occur in January and February of 2021; there are also a few
visible per season from other southern locations.

The Rossiter-McLaughlin approach is more likely to yield short-term
success than a direct mass measurement because of the RV noise
expected to be induced by stellar rotation.  The photometric amplitude
induced by starspots on \tn\ is $\approx 2\%$. 
The RV noise expected over the course of the $\approx 3\,{\rm d}$
rotation period can then be estimated by multiplying the photometric amplitude and
spectroscopic equatorial velocity.  This gives $\sigma_{\rm RV,rot}
\approx 300\,{\rm m\,s}^{-1}$, and is consistent with the scatter we
observe in our radial velocities from FEROS.  Detecting
a planet's Doppler signal in these regimes is
challenging, and requires a significant amount of data and care in
signal extraction \citep{barragan_radial_2019}.  The
Rossiter-McLaughlin measurement avoids the majority of this issue
because the transit occurs over a much shorter duration than a single
stellar rotation period.

If the RM measurements prove that the planet
is real, a campaign to measure the mass timed to coincide with
TESS sectors 36 and 37 ({\it i.e.}, from late March to late May of
2021) would significantly ease the extraction of the planetary Doppler
signal.  The reason is that the radial velocities, activity
indicators, and photometry could then be fit simultaneously, which
would greatly constrain any gaussian process model for the
spot-induced RV signal.
